Relating two Abstractions for Formal Array Languages

### 2014-04-11 paper.tex
An abstract

\begin{abstract}
This is the text of the abstract.
\end{abstract}

>>>>

\begin{abstract}
The aim of this paper is to rectify some of the fragmentation
high-performance array programming community. We look at two
formalisms for functional, high-performance array computations:
Mathematics of Arrays and Pull arrays.  On the surface they appear
rather different but at their core they share many principles and
properties.  In this paper we spell out the striking similarities
between these two formalisms. This paper is meant as a guide for
researchers knowledgeable in one of the formalisms who would like to
learn about the other.

\end{abstract}
